Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-03-09 Paper/Manuscript_Stats&Comp/reply_letter_STCO.tex
Minor edits to first part of reply letter

\item The analysis has been extended to the Mat\'ern-5/2 kernel. So the whole study provides the explicit diagnostic for a squared exponential, Mat\'ern-3/2, Mat\'ern-5/2 (Sections 4.3 and 4.3.1), and periodic squared exponential (Sections 3.3, 4.4 and Appendix C) covariance functions. In addition connection to other covariance functions is discussed.

@@

\item We have derived numerical equations that characterize the relationships between the hyperparameters of the model for each particular kernel, which are useful to update and find out optimal values for the hyper-parameters (Section 4.3.1).

@@

\item We have added a new case study to Section 5 which consists of a wiggly 2D simulated data set, demonstrating the applicability and usefulness of the diagnostic tool in multidimensional cases. Additional results concerning computational cost in 2D, 3D and 4D have been presented and briefly discussed, emphasizing that applying the diagnostic tool allows for minimum computational requirements that can be essential for very large data sets, multi-dimensional cases, or other problems that require repeated fitting.

>>>>

\item The analysis has been extended to the Mat\'ern-5/2 kernel. So the whole study provides the explicit diagnostic for a squared exponential, Mat\'ern-3/2, Mat\'ern-5/2 (Sections 4.3 and 4.3.1), and periodic squared exponential (Sections 3.3, 4.4 and Appendix C) covariance functions. In addition, the connection to other covariance functions is discussed.

@@

\item We have derived numerical equations that characterize the relationships between the hyperparameters of the model for each particular kernel, which are useful to update and determine optimal values for the hyper-parameters (Section 4.3.1).

@@

\item We have added a new case study to Section 5 which consists of a wiggly 2D simulated data set, demonstrating the applicability and usefulness of the diagnostic tool in multidimensional cases. Additional results concerning the computational cost in 2D, 3D and 4D have been presented and briefly discussed, emphasizing that the diagnostic facilitates a reduction of the required computational ressources, which can be essential for very large data sets, multi-dimensional cases, or other problems that require repeated fitting.
